Dependent Object Types

### 2012-08-05 article.tex
rewording

We need to be able to relate path-dependent types after reduction. The
original DOT calculus doesn't have any rules for dealing with
path-equality. Here is an example which motivates the need for
path-equality provisions.

@@

$a.i.l$ reduces to $b.l$. $b.l$ has type $b.X$, so we need $b.X <:
a.i.X$. This cannot be established with the current rules: it is not
true in general, but true here because $a.i$ reduces to $b$. Hence,
the need for acknowledging path equality.

>>>>

For preservation, we need to be able to relate path-dependent types
after reduction. Here is a motivating example:

@@

$a.i.l$ reduces to $b.l$. $b.l$ has type $b.X$, so we need $b.X <:
a.i.X$. This cannot be established with the current rules: it is not
true in general, but true here because $a.i$ reduces to $b$. Hence,
the need for acknowledging path equality for preservation to hold.
